---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pythonicr -- *Pythonic R*

<!-- badges: start -->
<!-- badges: end -->

A collection of packages that aims to reduce the learning curve for Python users
venturing into R and to keep myself from asking, "How do I do that in R again?"

## Installation

Unfortunately, I have not put anythying on CRAN yet. One day, I will but it 
could be a little while. Until then you can install the development version of 
pythonicr from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("pythonicr/pythonicr")
```

To install all of the available packages:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("pythonicr/pythonicr")
pythonicr::pythonicr_install_packages()
```

## Getting started

Each *pythonicr* package has its own purpose, so the best way to get started is
by poking around and seeing what might be useful to you.

- [**pathlib**](https://pythonicr.github.io/pathlib/): Python-ish path manipulations
- [**re**](https://pythonicr.github.io/re/): Python-ish regular expressions
- [**sets**](https://pythonicr.github.io/sets/): Python-ish set operations
- [**strs**](https://pythonicr.github.io/strs/): Python-ish string manipulations


## Dependencies

Most of the packages are wrappers for more mature R packages. That said, I have
tried to keep the dependencies to a minimum.


## Contributing

I happy to receive bug reports, suggestions, questions, and (most of all) 
contributions to fix problems and add features. Pull Requests for contributions 
are encouraged.

Here are some simple ways in which you can contribute (in the increasing order 
of commitment):

- Read and correct any inconsistencies in the documentation
- Raise issues about bugs or wanted features
- Review code
- Add new functionality

